An Introduction to Rocker: Docker Containers for R

### 2016-12-14 manuscript.Rmd

---
title: "An Introduction to Rocker: Docker Containers for R"
author:
  - name: Carl Boettiger
    affiliation: UC Berkeley 
    address:
    - ESPM Department, University of California,
    - 130 Mulford Hall Berkeley, CA 94720-3114, USA
    email:  cboettig@berkeley.edu
  - name: Dirk Eddlebuettel
    affiliation: Debian, ...
    address:
    - line 1
    - line 2
    email:  edd@debian.org
abstract: >
  We describe the Rocker project, which provides a widely used suite of Docker images
  with customized R environments for particular tasks. We discuss how this suite is
  organized and how these tools can increase portability, scaling, reproducibility,
  and convenience of R users and developers.
preamble: >
  % Any extra latex you need in the preamble
output: rticles::rjournal_article
---

@@

```bash
wget -qO- https://get.docker.com/ | sh
sudo docker run -d -p 80:8787 -e PASSWORD=<PICK-A-PASSWORD> rocker/rstudio
```

>>>>

---
title: "An Introduction to Rocker: Docker Containers for R"
author:
  - name: Carl Boettiger
    affiliation: UC Berkeley 
    address:
    - ESPM Department, University of California,
    - 130 Mulford Hall Berkeley, CA 94720-3114, USA
    email:  cboettig@berkeley.edu
  - name: Dirk Eddelbuettel
    affiliation: Debian and R Projects
    address:
    - line 1
    - line 2
    email:  edd@debian.org
abstract: >
  We describe the Rocker project, which provides a widely used suite of Docker images
  with customized R environments for particular tasks. We discuss how this suite is
  organized and how these tools can increase portability, scaling, reproducibility,
  and convenience of R users and developers.
preamble: >
  % Any extra latex you need in the preamble
output: rticles::rjournal_article
---

@@

```
wget -qO- https://get.docker.com/ | sh
sudo docker run -d -p 80:8787 -e PASSWORD=<PICK-A-PASSWORD> rocker/rstudio
```
